A Fundamental Measure Theory Functional for Hard-Sphere Contact Densities

### 2011-09-26 paper/project.tex

The majority of the empirical parameters used in our functional are
taken from the paper of Clark \emph{et al} on developing an optimal
SAFT model for water\cite{clark2006developing}.  This SAFT model
contains five empirical parameters: the hard-sphere radius, an energy
and length scale for the dispersion interaction, and an energy and
length scale for the association interaction.  In addition to the five
empirical parameters of Clark \emph{et al}, we add a single additional
parameter $\sigma$ defining the length scale over which the density is averaged
when computing the dispersion free energy.  We use this final
parameter to fit the surface tension, with the result shown in
Figure~\ref{fig:surface-tension}.  Because the SAFT model of Clark
\emph{et al} overestimates the critical temperature---which is a
common feature of models which do not explicitly treat the critical
point---we cannot correctly describe the surface tension at all
temperatures, and chose to fit it for the temperature range at which
water is liquid at one atmosphere of pressure.

>>>>

The majority of the empirical parameters used in our functional are
taken from the paper of Clark \emph{et al} on developing an optimal
SAFT model for water\cite{clark2006developing}.  This SAFT model
contains five empirical parameters: the hard-sphere radius, an energy
and length scale for the dispersion interaction, and an energy and
length scale for the association interaction.  In addition to the five
empirical parameters of Clark \emph{et al}, we add a single additional
parameter $\lscale$---with a fitted value of 0.72---which determines
the length scale over which the density is averaged when computing the
dispersion free energy.  We use this final parameter to fit the
surface tension, with the result shown in
>>>>>>> 92fcd98014a991adc9e2804a16040e70e2b2bfcb
Figure~\ref{fig:surface-tension}.  Because the SAFT model of Clark
\emph{et al} overestimates the critical temperature---which is a
common feature of models which do not explicitly treat the critical
point---we cannot correctly describe the surface tension at all
temperatures, and chose to fit it for the temperature range at which
water is liquid at one atmosphere of pressure.

### 2011-09-26 papers/contact/paper.tex

>>>>

\begin{figure}
  \includegraphics[height=5cm]{figs/contact-08-013}
  \caption{Density and contact densities of thirteen hard spheres in a
    spherical cavity with diameter 8.}
  \label{fig:sphere-8}
\end{figure}

\begin{figure}
  \includegraphics[height=5cm]{figs/contact-12-112}
  \caption{Density and contact densities of 112 hard spheres in a
    spherical cavity with diameter 12.}
  \label{fig:sphere-12}
\end{figure}

\begin{figure}
  \includegraphics[height=5cm]{figs/contact-16-265}
  \caption{Density and contact densities of 265 hard spheres in a
    spherical cavity with diameter 16.}
  \label{fig:sphere-16}
\end{figure}
